\begin{formal}
          
          \begin{quote}
          
                    The Center for Internet Security (CIS) Critical Security Controls (CSC) is a set of best practices and guidelines designed to help organizations enhance their cybersecurity defenses and reduce the risk of cyber threats. The CIS CSC provides a prioritized and actionable security control framework that organizations can implement to improve their overall security posture. The CIS CSC consists of 20 specific controls that cover a wide range of cybersecurity areas, including asset management, secure configuration, continuous vulnerability management, and incident response. These controls are based on real-world attack patterns and are regularly updated to address emerging threats and vulnerabilities. The controls are organized into three implementation groups: Basic, Foundational, and Organizational, which represent progressive levels of security maturity and coverage. The CIS CSC is a valuable resource for organizations looking to establish a solid foundation of cybersecurity controls. It provides practical and effective measures that can be implemented to mitigate common security risks and enhance the organization's ability to detect, respond to, and recover from cyber incidents. The controls are designed to be adaptible to various environments. They can be tailored to meet organizations' specific needs and requirements.
                    
                    \begin{flushright}
                            ---\cite{boyle2023}
                    \end{flushright}
                    
          \end{quote}
          
\end{formal}